HPC--101\\Onboarding

### 2023-04-30 hpc_101/sections/01_intro.tex
update the slides to contain updated info.
Group/lab storage creation point

\section[Terminology]{Terminology}

\begin{frame}
	\frametitle{Terminology}
	\begin{itemize}
	\item \textbf{Node} -- Another name for a server or computer
        \item \textbf{Login node} -- A specialized node that users connect to in order to submit work to a computer cluster
        \item \textbf{Computer cluster} -- A set of loosely or tightly connected nodes that work together so that, in many respects, they can be viewed as a single system\footnote{\label{wiki_ccluster}\tiny\url{https://en.wikipedia.org/wiki/Computer_cluster}}
        \item \textbf{Data transfer node (DTN)} -- Specialized nodes that minimize the impedance on the network to access the full capability of the network
	\item \textbf{Science DMZ (SciDMZ)} --  A portion of the network configured with equipment and security policies in order to optimize for high-performance scientific applications rather than for general-purpose business systems or “enterprise” computing 
	\item \textbf{Multi-factor Authentication (MFA)} -- An authentication method in which a computer user is granted access only after successfully presenting two or more pieces of evidence or factors to an authentication mechanism, e.g., DUO

	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Terminology}
	\begin{itemize}
	\item \textbf{Symbolic Link (symlink)} -- A file that contains a reference to another file or directory
	\item \textbf{Command-line interface/interpreter (CLI)} -- A text-based user interface used to view and manage computer files 
	\item \textbf{Message Passing Interface (MPI)} -- A standard that is used by programs to pass messages between nodes
	\item \textbf{High Performance Compute (HPC)} -- A computing paradigm in which applications are typically a tightly coupled parallel job that benefit from a low-latency interconnect
	\item \textbf{High Throughput Compute (HTC)} -- A computing paradigm that focuses on the efficient execution of a large number of loosely-coupled tasks
        \item \textbf{Modified time} -- The last time the file was modified (content has been modified)\footnote{\label{Types of timestamps}\tiny\url{https://unix.stackexchange.com/a/2465}}
        \item \textbf{Shell script (script)} -- A computer program designed to be run by a CLI\footnote{\label{Shell script}\tiny\url{https://en.wikipedia.org/wiki/Shell_script}}
%        \item Pleasantly Parallel -- Processes are independent and no communication is necessary 
	\end{itemize}

@@

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 346                    & 8,500                      & 63.2 TB                   &  120                   & 80 TB                             &  111 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on {\mana}
    \end{itemize}
  \item Group/Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Group/Lab storage allows users to share data \& applications with a need for persistence on {\mana}
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on {\mana} have the following attributes:
  \begin{itemize}
  \item 50 GB default quota with a max quota of 300 GB
  \item Quota increases are re-evaluated annually
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& User Guide prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our User Guide.~\\
		\begin{itemize}
		\item \href{http://datascience.hawaii.edu/hpc/}{Information \& policies}
		\item \href{http://go.hawaii.edu/JLA}{Resource Documentation \& User Guide}
		\item \href{http://go.hawaii.edu/3A8}{Video Tutorials}
		\end{itemize}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu

>>>>

@@

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 366                    & 9,396                      & 67.3 TB                   &  120                   & 80 TB                             &  111 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on {\mana}
    \end{itemize}
  \item Group/Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Group/Lab storage allows users to share data \& applications with a need for persistence on {\mana}
    \item PI must contact \textbf{uh-hpc-help@lists.hawaii.edu} to set up group/lab storage
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on {\mana} have the following attributes:
  \begin{itemize}
  \item 50 GB default quota with a max quota of 300 GB
  \item Quota increases are re-evaluated annually
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& User Guide prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our User Guide.~\\
		\begin{itemize}
		\item \href{http://datascience.hawaii.edu/hpc/}{Information \& policies}
		\item \href{http://go.hawaii.edu/ex2}{Resource Documentation \& User Guide}
		\item \href{http://go.hawaii.edu/3A8}{Video Tutorials}
		\end{itemize}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu
